Trending assessment for nowcasts, measurements, and forecasts

### 2024-02-20 sections/02-notation.tex
Update on Overleaf.

While measurement series are created by recording data using measuring instruments or direct observation, forecasting focuses on predicting the future based on historical data and its patterns. We note in the following the real realizations of the target value with $(y_t)^T_{t=0}$ and the prediction data for a target variable can be organized in such a way that $x_{\tau|t}$ the prediction of one predictor for time $\tau$ at time $t$ provided that $\tau$ is greater than $t$. The forecast is for the future point in time $\tau$ and is based on the information available at time $t$. 
In practice, a forecasting method is typically evaluated by forecast accuracy, which is defined by a certain loss function and evaluates the difference between the forecast and the actual outcome of the target variable.
A comparison of several forecasters can then be made, for example, by ranking the forecast accuracies of the forecasters.
In practice, prediction accuracy is measured by scale-dependent measures such as the Root Mean Square Error (RMSE) or measures based on percentage errors such as the Root Mean Square Percentage Error (RMSPE). All of these typical measures are based on the absolute difference between forecast and true values, locally or globally. For an overview of different measures, see \cite{hyndman2006another}. 
In contrast to conventional forecasting methods, nowcasting focuses on predicting the current status and is therefore sometimes also referred to as short-term forecasting. \unsure[noinline]{Ich finde da wird der Unterschied noch nicht so richtig klar} Nowcasting has its origins in meteorology, and the methods were originally developed to describe the current state of the weather in detail and to predict the expected change on a time scale of a few hours (\cite{browning1989nowcasting,schmid2019nowcasting}).
Nowcasting focuses on predictions for the present, the immediate future, and the recent past, and is now being used in other fields such as economics and medicine. Nowcasting can be used to predict important statistics about the current economic situation that is only available with a considerable time lag (\cite{banbura2013now, giannone2006nowcasting,fornaro2020nowcasting,bok2018macroeconomic}). In medicine, epidemic nowcasting is used during an ongoing epidemic to assess the current situation, taking into account the main pathogenic, epidemiological, clinical, and socio-behavioral factors (\cite{wu2021nowcasting}). For possible applications in this area, see \cite{johansson2014nowcasting,gunther2021nowcasting,birrell2021real}.
When predicting values in the present, it is usual that the true values of the recent past are not available, so only an estimate of these values is provided by the nowcast. For example, the current number of cases of an infectious disease may not be immediately available due to delays in data collection or reporting, or the situation may change rapidly so that the reported figures become inaccurate very quickly.
Using the notation for forecasting above, this means that a prediction value $x_{\tau|t}$ also exits for $\tau$ less than or equal to $t$.
Similar to forecasting, nowcasts are often evaluated and compared in the literature on the basis of performance measures such as the root mean absolute error (\cite{gunther2021nowcasting}).

>>>>

While measurement series are created by recording data using measuring instruments or direct observation, forecasting focuses on predicting the future based on historical data and its patterns. We note in the following the real realizations of the target value with $(y_t)^T_{t=0}$ and the prediction data for a target variable can be organized in such a way that $x_{\tau|t}$ the prediction of one predictor for time $\tau$ at time $t$ provided that $\tau$ is greater than $t$. The forecast is for the future point in time $\tau$ and is based on the information available at time $t$. 
In practice, a forecasting method is typically evaluated by forecast accuracy, which is defined by a certain loss function and evaluates the difference between the forecast and the actual outcome of the target variable.
A comparison of several forecasters can then be made, for example, by ranking the forecast accuracies of the forecasters.
In practice, prediction accuracy is measured by scale-dependent measures such as the Root Mean Square Error (RMSE) or measures based on percentage errors such as the Root Mean Square Percentage Error (RMSPE). All of these typical measures are based on the absolute difference between forecast and true values, locally or globally. For an overview of different measures, see \cite{hyndman2006another}. 
In contrast to conventional forecasting methods, nowcasting focuses on predicting the current status and is therefore sometimes also referred to as short-term forecasting. \unsure[noinline]{Ich finde da wird der Unterschied noch nicht so richtig klar} Nowcasting has its origins in meteorology, and the methods were originally developed to describe the current state of the weather in detail and to predict the expected change on a time scale of a few hours (\cite{browning1989nowcasting,schmid2019nowcasting}).
Nowcasting focuses on predictions for the present, the immediate future, and the recent past, and is now being used in other fields such as economics and medicine. For example, Nowcasting can be used to predict important statistics about the current economic situation that is only available with a considerable time lag (\cite{banbura2013now, giannone2006nowcasting,fornaro2020nowcasting,bok2018macroeconomic}). In medicine, epidemic nowcasting is used during an ongoing epidemic to assess the current situation, taking into account the main pathogenic, epidemiological, clinical, and socio-behavioral factors (\cite{wu2021nowcasting}). For possible applications in this area, see \cite{johansson2014nowcasting,gunther2021nowcasting,birrell2021real}.
When predicting values in the present, it is usual that the true values of the recent past are not available, so only an estimate of these values is provided by the nowcast. For example, the current number of cases of an infectious disease may not be immediately available due to delays in data collection or reporting, or the situation may change rapidly so that the reported figures become inaccurate very quickly.
Using the notation for forecasting above, this means that a prediction value $x_{\tau|t}$ also exits for $\tau$ less than or equal to $t$.
Similar to forecasting, nowcasts are often evaluated and compared in the literature on the basis of performance measures such as the root mean absolute error (\cite{gunther2021nowcasting}).
